Fluent statistical computing interfaces for biological data analysis

### 2020-08-03 Rmd/06-conclusion.Rmd
spelling

A limitation of the grammar as we have implemented it in 
**plyranges** is lack of scalability and computational speed for data sets
that do not fit in memory. We attempted several techniques for performing 
delayed operations over range-based data, however a more general approach
that allows for data stored on the cloud or in scientific data formats
like HDF5 that leverage existing Bioconductor frameworks would be useful.
We showed in chapters \@ref(ch:fluentGenomics) ad \@ref(ch:intron) that an
analyst is able to do some very complex data transformations and re-sampling 
procedures via casting results into _GRanges_ object. However, it is unclear 
whether the semantics of our grammar can be extended to data that can not be 
effeciently reshaped into long form tidy representations. Moreover, further work
is required to explore the design space of grammars for data 
transformations and grammars for graphics when the data are large, multifaceted
and non-rectangular.

>>>>

A limitation of the grammar as we have implemented it in 
**plyranges** is lack of scalability and computational speed for data sets
that do not fit in memory. We attempted several techniques for performing 
delayed operations over range-based data, however a more general approach
that allows for data stored on the cloud or in scientific data formats
like HDF5 that leverage existing Bioconductor frameworks would be useful.
We showed in chapters \@ref(ch:fluentGenomics) ad \@ref(ch:intron) that an
analyst is able to do some very complex data transformations and re-sampling 
procedures via casting results into _GRanges_ object. However, it is unclear 
whether the semantics of our grammar can be extended to data that can not be 
efficiently reshaped into long form tidy representations. Moreover, further work
is required to explore the design space of grammars for data 
transformations and grammars for graphics when the data are large, multifaceted
and non-rectangular.
